---
title: "Publications"
---

```{r load}
library("RefManageR")
source("R/refman_style.R")
bib <- ReadBib("media/papers.bib")

for(i in 1:length(bib)){
  bib[[i]]$pages <- gsub("(?<!-)-(?!-)", "--", gsub(" ", "", bib[[i]]$pages), perl = TRUE)
}

```

::: panel-tabset
### Journal Articles

```{r papers, results = "asis"}

papers <- bib[bib$bibtype == "Article"]

NoCite(papers)
PrintBibliography(papers, .opts = list(style = "markdown", sorting = "ydnt", max.names = Inf, no.print.fields = c("number", "eprint", "issn", "isbn", "url", "month", "date")))
```

Number of papers: `r sum(bib$bibtype == "Article")`\

### Presentations and Posters

```{r conferences, results = "asis"}

conference <- ReadBib("media/post_conf.bib")

NoCite(conference)
PrintBibliography(conference, .opts = list(style = "markdown", sorting = "ydnt", max.names = 20, no.print.fields = c("ISSN", "month", "date")))
```

### Others

```{r other, results = "asis"}

other <- bib[bib$bibtype != "Article"]

NoCite(other)
PrintBibliography(other, .opts = list(style = "markdown", sorting = "ydnt", max.names = Inf, no.print.fields = c("number", "eprint", "issn", "isbn", "url", "month", "date")))
```

### Thesis

- **Unraveling the complexity of plant community responses to climate change**\ (2023)
*Supervised by: [John Arvid Grytnes](https://www.researchgate.net/profile/John_Arvid_Grytnes),* [*Suzette Flantua*](https://www.researchgate.net/profile/Suzette_Flantua) and [*Fride Høistad Schei*](https://www.researchgate.net/profile/Fride_Schei) *PhD thesis*. University of Bergen

-   **Pacheco-Riaño, L.C.** (2018). Assessing the impact of fragmentation on plant dispersal in Andean mountains. *Master thesis*. University of Amsterdam.
-   **Pacheco-Riaño, L.C.** (2018). Changing land use cover patterns after intensification of the irrigated agriculture in the Rio Grande River watershed – Spain. *Master thesis*. University of Amsterdam.
-   **Pacheco-Riaño, L.C.** (2015). Bird communities, their functional groups and ecosystem services in a Colombian coffee landscape.*Bachelor's thesis*. Pontificia Universidad Javeriana .
:::

::: callout-important
Enhanced references courtesy of [Richardjtelford's](https://github.com/richardjtelford/richardjtelford.github.io/) repository.
:::
