---
title: "Publications"
---

```{r load}
library("RefManageR")
source("R/refman_style.R")
bib <- ReadBib("media/papers.bib")

biblio_opts <- list(
  style = "markdown",
  sorting = "ydnt",
  max.names = Inf,
  no.print.fields = c("number", "eprint", "issn", "isbn", "url", "month", "date")
)

```

::: panel-tabset
### Journal Articles

```{r papers, results = "asis"}
papers <- SearchBib(bib, bibtype = "Article")
NoCite(papers)
PrintBibliography(papers, .opts = biblio_opts)
```

Number of papers: `r sum(bib$bibtype == "Article")`\

### Presentations and Posters

```{r conferences, results = "asis"}

conference <- ReadBib("media/post_conf.bib")

NoCite(conference)
PrintBibliography(conference, .opts = list(style = "markdown", sorting = "ydnt", max.names = 20, no.print.fields = c("ISSN", "month", "date")))
```

### Others

```{r other, results = "asis"}

other <- bib[bib$bibtype != "Article"]

NoCite(other)
PrintBibliography(other, .opts = list(style = "markdown", sorting = "ydnt", max.names = Inf, no.print.fields = c("number", "eprint", "issn", "isbn", "url", "month", "date")))
```

### Thesis

-  **Pacheco-Riaño, L.C.** (2023). Unraveling the complexity of plant community responses to climate change.
*Supervised by: [John Arvid Grytnes](https://www.researchgate.net/profile/John_Arvid_Grytnes),* [*Suzette Flantua*](https://www.researchgate.net/profile/Suzette_Flantua) and [*Fride Høistad Schei*](https://www.researchgate.net/profile/Fride_Schei) *PhD thesis*. University of Bergen

-   **Pacheco-Riaño, L.C.** (2018). Assessing the impact of fragmentation on plant dispersal in Andean mountains. *Master thesis*. University of Amsterdam.
-   **Pacheco-Riaño, L.C.** (2018). Changing land use cover patterns after intensification of the irrigated agriculture in the Rio Grande River watershed – Spain. *Master thesis*. University of Amsterdam.
-   **Pacheco-Riaño, L.C.** (2015). Bird communities, their functional groups and ecosystem services in a Colombian coffee landscape.*Bachelor's thesis*. Pontificia Universidad Javeriana .
:::
