---
title: "Publications"
description: "Peer-reviewed journal articles, conference presentations, and thesis work."
---

```{r load}
library("RefManageR")
source("R/refman_style.R")
bib <- ReadBib("media/papers.bib")

biblio_opts <- list(
  style = "markdown",
  sorting = "ydnt",
  max.names = Inf,
  no.print.fields = c("number", "eprint", "issn", "isbn", "url", "month", "date")
)

```

<style>
.authors-toggle {
  cursor: pointer;
  font-size: 0.92em;
  font-weight: 600;
  white-space: nowrap;
}

.authors-toggle:hover,
.authors-toggle:focus {
  text-decoration: underline;
}
</style>

<script>
document.addEventListener("DOMContentLoaded", function () {
  document.querySelectorAll(".authors-wrap").forEach(function (wrap) {
    var collapsed = wrap.querySelector(".authors-collapsed");
    var full = wrap.querySelector(".authors-full");
    if (!collapsed || !full) return;

    wrap.querySelectorAll(".authors-toggle").forEach(function (toggle) {
      var toggleAuthors = function () {
        var isCollapsed = full.style.display === "none";
        collapsed.style.display = isCollapsed ? "none" : "";
        full.style.display = isCollapsed ? "" : "none";
      };

      toggle.addEventListener("click", toggleAuthors);
      toggle.addEventListener("keydown", function (event) {
        if (event.key === "Enter" || event.key === " ") {
          event.preventDefault();
          toggleAuthors();
        }
      });
    });
  });
});
</script>
::: panel-tabset
### Journal Articles

```{r papers, results = "asis"}
papers <- SearchBib(bib, bibtype = "Article")
NoCite(papers)
PrintBibliography(papers, .opts = biblio_opts)
```

Number of papers: `r sum(bib$bibtype == "Article")`\

### Presentations and Posters

```{r conferences, results = "asis"}

conference <- ReadBib("media/post_conf.bib")

NoCite(conference)
PrintBibliography(conference, .opts = list(style = "markdown", sorting = "ydnt", max.names = 20, no.print.fields = c("ISSN", "month", "date")))
```

### Others

```{r other, results = "asis"}

other <- bib[bib$bibtype != "Article"]

NoCite(other)
PrintBibliography(other, .opts = list(style = "markdown", sorting = "ydnt", max.names = Inf, no.print.fields = c("number", "eprint", "issn", "isbn", "url", "month", "date")))
```

### Thesis

-  **Pacheco-Riaño, L.C.** (2023). Unraveling the complexity of plant community responses to climate change.
*Supervised by: [John Arvid Grytnes](https://www.researchgate.net/profile/John_Arvid_Grytnes),* [*Suzette Flantua*](https://www.researchgate.net/profile/Suzette_Flantua) and [*Fride Høistad Schei*](https://www.researchgate.net/profile/Fride_Schei) *PhD thesis*. University of Bergen

-   **Pacheco-Riaño, L.C.** (2018). Assessing the impact of fragmentation on plant dispersal in Andean mountains. *Master thesis*. University of Amsterdam.
-   **Pacheco-Riaño, L.C.** (2018). Changing land use cover patterns after intensification of the irrigated agriculture in the Rio Grande River watershed – Spain. *Master thesis*. University of Amsterdam.
-   **Pacheco-Riaño, L.C.** (2015). Bird communities, their functional groups and ecosystem services in a Colombian coffee landscape.*Bachelor's thesis*. Pontificia Universidad Javeriana .
:::
